Actuator line modeling of vertical-axis turbines

### 2016-05-02 paper.tex
Define solidity

Very fast solution times can be obtained with blade element momentum (BEM)
models, such as the double multiple streamtube (DMST) approached developed by
Paraschivoiu~\cite{Para1988}. However, their poor performance for high solidity
(or chord-to-radius ratio $c/R$) turbines \cite{Joo2015}, makes them less
attractive, particular for marine hydrokinetic applications, where rotors of the
same size will encounter approximately an order of magnitude higher torque
compared to wind turbines. Their description of the flow field is very crude as
well, simply computing the momemtum contained within discretized streamtubes,
which cannot resolve any of the complicated flow structures shed by the rotor.

>>>>

Very fast solution times can be obtained with blade element momentum (BEM)
models, such as the double multiple streamtube (DMST) approached developed by
Paraschivoiu~\cite{Para1988}. However, their poor performance for rotors with
high solidity~\cite{Joo2015} $Nc/R$ (and/or chord-to-radius ratio $c/R$), where
$N$ is the number of blades, $c$ is the chord length, and $R$ is the maximum
rotor radius, makes them less attractive, particular for marine hydrokinetic
applications where rotors of the same size will encounter approximately an order
of magnitude higher torque compared to wind turbines. Their description of the
flow field is very crude as well, simply computing the momentum contained within
discretized streamtubes, which cannot resolve any of the complicated flow
structures shed by the rotor.
